Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-10-29 doc/paper.Rmd
some information on profiles and how they are being used in the chumbley algorithm _.

Coming back to the database of Hamby 44 and Hamby 252 datasets, the run_id = 3 was used when applying the chumbley algorithm on the signatures. The run_id not only defines the level of smoothing but also signifies the chosen height at which the profiles were selected initially.
Another important aspect is the range of horizontal values (which is referred to as the y values in \citet{aoas}) in the signatures. Thes have already been pre-processed in the database to not include any grooves.

@@

The idea therefore is to first use these raw values of the profile directly in the chumbley algorithm, and see how the algorithm performs for different coarseness values (smoothing parameter as referred in the function LOWESS used in the chumbley algorithm).

>>>>

Coming back to the database of Hamby-44 and Hamby-252 datasets, the run_id = 3 was used when applying the chumbley algorithm on the signatures. The run_id not only defines the level of smoothing but also signifies the chosen height at which the profiles were selected initially.
Another important aspect is the range of horizontal values (which is referred to as the y values in \citet{aoas}) in the signatures. Thes have already been pre-processed in the database to not include any grooves.

@@

The idea therefore is to first use these raw values of the profile directly in the chumbley algorithm, and see how the algorithm performs for different coarseness values (smoothing parameter as referred in the function LOWESS used in the chumbley algorithm)
